COVID-19 Policy-Compliance in Europe

### 2020-12-24 Draft.Rmd
Changed html to pdf output

---
title: "COVID-19 Policy-Compliance in Europe"
author: "Philipp Holz"
date: 'December 24, 2020'
output:
  github_document:
    toc: true
    keep_html: true
bibliography: References.json

@@

H₀: There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.

Hₐ: There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.

@@

`Compliance Index = β₀ + β₁ × Date + β₂ × Country + β₃ × Publicity + β₄ × Cases per 100.000 per 14 days + ε`

@@

# Generate regression table
texreg::htmlreg(lm1, single.row = TRUE, 
#                         custom.header = list("Model Results" = 1),
#                         model.names = c("My name 1", "My name 2"), 
                         custom.coef.names = c("Intercept", "Date", "Publicity",
                                               "Cases/100,000/14 Days",
                                               "Belgium",
                                               "Denmark",
                                               "France",
                                               "Germany",
                                               "Ireland",
                                               "Italy",
                                               "Netherlands",
                                               "Poland",
                                               "Spain",
                                               "Sweden",
                                               "United Kingdom"),
                          bold = 0.05,
                          center = TRUE,
                          caption = "Regression Table"
                         )
```

>>>>

---
title: "COVID-19 Policy-Compliance in Europe"
author: "Philipp Holz"
date: 'December 24, 2020'
output: pdf_document
bibliography: References.json

@@

H(null): There **is no** difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does not** express a trend.

H(alternative): There **is** a difference in compliance with mobility-reducing policies in Europe and this policy-compliance **does** express a trend.

@@

@@

# Generate regression table
texreg::texreg(lm1, single.row = TRUE, 
#                         custom.header = list("Model Results" = 1),
#                         model.names = c("My name 1", "My name 2"), 
                         custom.coef.names = c("Intercept", "Date", "Publicity",
                                               "Cases/100,000/14 Days",
                                               "Belgium",
                                               "Denmark",
                                               "France",
                                               "Germany",
                                               "Ireland",
                                               "Italy",
                                               "Netherlands",
                                               "Poland",
                                               "Spain",
                                               "Sweden",
                                               "United Kingdom"),
                          bold = 0.05,
                          center = TRUE,
                          caption = "Regression Table"
                         )
```
